Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-23 paper.qmd
Updated Figure 9 (d)

benchmark_label_df <- tibble(y = benchmark_scurve - 0.03,
                             x = 1.3,
                             label = paste0("benchmark is ", benchmark_scurve))

## To draw the distance distribution
distance_scurve$group <- "1"
distance_scurve_plot <- ggplot(distance_scurve, 
                        aes(x = group, 
                            y = distance)) + 
  geom_quasirandom(
    size = 2, 
    alpha = 0.3
  ) + 
  ylim(0, max(unlist(distance_scurve$distance))+ 0.5) + 
  coord_flip() + 
  geom_hline(yintercept = benchmark_scurve,
     linetype="solid", 
     color = "black", linewidth=0.5, alpha = 0.5) +
  ylab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        plot.title = element_text(size = 12))

# Define bin width and starting point
bin_width <- hb_obj_scurve2$centroids$c_x[2]-hb_obj_scurve2$centroids$c_x[1]
start_point <- bin_width/2

@@

distance_hist <- ggplot(
  distance_scurve, aes(x = distance)) +
    geom_histogram(
      aes(y = after_stat(count) / sum(after_stat(count))), 
      binwidth = bin_width) +
  scale_x_continuous(breaks = bin_labels, labels = round(bin_labels, 2)) +
  ylab("standardized number of edges") +
  xlab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

distance_scurve_summary <- distance_scurve |>
  group_by(bin) |>
  summarise(count = n()) |>
  mutate(std_counts = count/sum(count))

>>>>

benchmark_label_df <- tibble(
  y = benchmark_scurve - 0.03, 
  x = 1.3, 
  label = paste0("benchmark is ", benchmark_scurve))

## To draw the distance distribution
# distance_scurve$group <- "1"
# distance_scurve_plot <- ggplot(distance_scurve, 
#                         aes(x = group, 
#                             y = distance)) + 
#   geom_quasirandom(
#     size = 2, 
#     alpha = 0.3
#   ) + 
#   ylim(0, max(unlist(distance_scurve$distance))+ 0.5) + 
#   coord_flip() + 
#   geom_hline(yintercept = benchmark_scurve,
#      linetype="solid", 
#      color = "black", linewidth=0.5, alpha = 0.5) +
#   ylab(expression(d^{(2)})) +
#   ggtitle("(d)") +
#   theme(aspect.ratio = 0.75,
#         axis.text.x = element_text(size = 12),
#         axis.title.x = element_text(size = 12),
#         plot.title = element_text(size = 12))

# Define bin width and starting point
bin_width <- hb_obj_scurve2$a1
start_point <- bin_width/2

@@

distance_hist <- ggplot(
  distance_scurve, aes(x = distance)) +
    geom_histogram(
      aes(y = after_stat(count) / sum(after_stat(count))), 
      binwidth = bin_width) +
  scale_x_continuous(breaks = bin_labels, 
                     labels = c(
                       expression(a[1]),
                       expression(2*a[1]),
                       expression(3*a[1]),
                       expression(4*a[1]),
                       expression(5*a[1]),
                       expression(6*a[1]),
                       expression(7*a[1]),
                       expression(8*a[1]),
                       expression(9*a[1]),
                       expression(10*a[1]),
                       expression(11*a[1]),
                       expression(12*a[1]),
                       expression(13*a[1])
                     )) +
  # geom_text(
  #   data = tibble(x = 12*bin_width, y = 0.7,
  #                 text = expression(a[1])),
  #   aes(
  #     x=x,
  #     y=y,
  #     label = text
  #   )
  # 
  # ) +
  geom_vline(xintercept = start_point + 2*bin_width,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  ylab("Proportion of the number of edges") +
  xlab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

# distance_scurve_summary <- distance_scurve |>
#   group_by(bin) |>
#   summarise(count = n()) |>
#   mutate(std_counts = count/sum(count))
